Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-26 paper/Draft.tex
Debugged outliers of SPF that caused weired results for individual SPF. it was not so for Pop because I used the correct data.
Created positions for inf-var charts. polishing regression tables. mostly finished.

\begin{figure}[h]\label{ir_pop}
	\centering
	\includegraphics[width=14cm]{figures/ir_popseni.png} 
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

@@

The left  three figures look into the relationship between forecast error and uncertainty. In general, one may expect that  greater ex ante uncertainty implies greater ex post forecast errors.

@@

\begin{figure}[h]\label{UnceratitnyOtherMoments}
	\centering
	\includegraphics[width=6cm]{figures/fe_var2Q.png}
	\includegraphics[width=6cm]{figures/var_disg2Q.png}\\
	\smallskip
	\includegraphics[width=6cm]{figures/fe_var3Q.png}
	\includegraphics[width=6cm]{figures/var_disg3Q.png}\\
	\smallskip	
	\includegraphics[width=6cm]{figures/fe_var.png}
	\includegraphics[width=6cm]{figures/var_disg.png}\\
		\caption{Unceratinty and Other Moments}
\end{figure}

@@

\begin{figure}[h]\label{Unceratitny_Histogram}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/PRCPCEMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEMean1_hist.png} 
	\includegraphics[width=6cm]{figures/SCEVar1_hist.png}  \\
	\caption{Distribution of Mean Forecast and Uncertainty }
\end{figure}

@@

>>>>

\begin{figure}[h]\label{ir_pop}
	\centering
	\includegraphics[width=15cm]{figures/ir_popseni.png} 
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

@@

The left  three figures look into the relationship between forecast error and uncertainty. One may expect that  greater ex ante uncertainty implies greater ex post forecast errors.

Another widely spoken fact is that uncertainty is positively correlated with the level of the inflation. We look this hypothesis by ploting uncertainty against the realized inflation.

@@

\begin{figure}[h]\label{UnceratitnyOtherMoments}
	\centering
		\centering
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf_var2Q.png}
	\includegraphics[width=3.5cm]{figures/fe_var2Q.png}
	\includegraphics[width=3.5cm]{figures/var_disg2Q.png}\\
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf_var3Q.png}
	\includegraphics[width=3.5cm]{figures/fe_var3Q.png}
	\includegraphics[width=3.5cm]{figures/var_disg3Q.png}\\
	\smallskip	
	\includegraphics[width=3.5cm]{figures/Inf_var.png}
	\includegraphics[width=3.5cm]{figures/fe_var.png}
	\includegraphics[width=3.5cm]{figures/var_disg.png}\\
		\caption{Unceratinty and Other Moments}
\end{figure}

@@

\begin{figure}[h]\label{Unceratitny_Histogram}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/PRCPCEMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEmean_hist.png} 
	\includegraphics[width=6cm]{figures/SCEvar_hist.png}  \\
	\caption{Distribution of Mean Forecast and Uncertainty }
\end{figure}

@@

\newpage

\begin{adjustbox}{angle=90}\label{RevEfficiency}
	\begin{tabular}{lllllllll}
		\hline 
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
		\hline 
		\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
	                                            \hline 
		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
		&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
		L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
		&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
		L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
		&               &           &          & (0.048)  &               &           &           & (0.069)   \\
		SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
		&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
		SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
		&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
		& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
		Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
		\hline 
		N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
		$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
		\hline 
		\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
		\hline 
		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
		&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
		L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
		&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
		L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
		&               &           &          & (0.121)  &               &           &           & (0.149)   \\
		Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
		& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
		\hline 
		N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
	$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
		\hline 
	\end{tabular}
\end{adjustbox}

\begin{adjustbox}{width={22cm},totalheight={12cm},angle=90}\label{WeakRevEfficiency}
	\begin{tabular}{llllllllllllll}
		\hline 
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
		\hline 
		\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
		\hline 
		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                      &               & (0.015)   & (0.022)   & (0.037)   \\
		L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
		&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                      &               &           & (0.021)   & (0.031)   \\
		L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
		&             &           &           & (0.032)   &               &           &           & (0.036)   &                      &               &           & (0.012)   & (0.027)   \\
		&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.025)   \\
		&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.018)   \\
		&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.012)   \\
		Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant               & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
		& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                      & (0.123)       & (0.110)   & (0.104)   & (0.163)   \\
		\hline 
		N                    & 1636        & 1430      & 1266      & 1141      & 1402          & 1190      & 1022      & 898       & N                    & 53016         & 43166     & 28850     & 14445     \\
	$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ & 0.000         & 0.182     & 0.278     & 0.321     \\
		\hline 
		\multicolumn{14}{l}{Test 4. Weak revision efficiency of change in uncertainty}                \\
		\hline                                                                                                                 
		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean change   & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean change   & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Var\_ch    &             & -0.393**  & -0.568*** & -0.543**  &               & -0.444*** & -0.602*** & -0.658*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
		&             & (0.136)   & (0.146)   & (0.177)   &               & (0.094)   & (0.127)   & (0.145)   &                      &               & -0.015    & -0.022    & -0.037    \\
		L2.InfExp\_Var\_ch   &             &           & -0.322**  & -0.278*   &               &           & -0.289*   & -0.404**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
		&             &           & (0.104)   & (0.132)   &               &           & (0.110)   & (0.137)   &                      &               &           & -0.021    & -0.031    \\
		L3.InfExp\_Var\_ch   &             &           &           & 0.048     &               &           &           & -0.292    & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
		&             &           &           & (0.096)   &               &           &           & (0.154)   &                      &               &           & -0.012    & -0.027    \\
		&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & -0.025    \\
		&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & -0.018    \\
		&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & -0.012    \\
		Constant               & -0.002      & -0.001    & 0.004     & 0.004     & 0.000         & 0.002     & 0.004     & 0.005     &   Constant                   & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
		& (0.005)     & (0.005)   & (0.004)   & (0.004)   & (0.004)       & (0.004)   & (0.004)   & (0.004)   &                      & -0.123        & -0.11     & -0.104    & -0.163    \\
		\hline 
		N                    & 1202        & 950       & 765       & 625       & 1078          & 842       & 657       & 519       &                      & 53016         & 43166     & 28850     & 14445     \\
		$R^2$ & 0.000       & 0.120     & 0.265     & 0.242     & 0.000         & 0.233     & 0.321     & 0.385     &                      & 0             & 0.182     & 0.278     & 0.321  \\
		\hline    
	\end{tabular}
\end{adjustbox}
